Tropical Mathematics and the Lambda Calculus

### 2023-01-24 section3new.tex
Mini commit

The tropical relational model is thus provided by the category $\LREL$ of matrices with values over $\Lawv$ (which, being a quantale, is indeed a continuous semi-ring).
%, where $\Lawv$ is the already introduced Lawvere quantale, seen as the idempotent complete semiring $(\BB R_{\geq0}\cup\set{\infty},\inf,\infty,+,0)$.
%The category $\LREL$ is well-defined because $\Lawv$ is a continuous semiring (w.r.t.\ its quantale order $\preceq$.
%This amounts to check that $\min$ and $+$ commute with the $\inf$ (as operations on $\BB R_{\geq0}\cup\set{\infty}$, which is immediate), and that $(\Lawv,\preceq)$ is a cpo with $\infty$ as bottom element (which is immediate since in $\Lawv$ we have $\vee = \inf$) .
It is worth observing that the formula for composition in $\LREL$ %is the tropicalisation of the one defining it in $\QREL$, i.e.
reads as \ $(st)_{a,c}:=\inf\limits_{b\in Y}\set{s_{b,c}+t_{a,b}}$;
 similarly, the linear functions $f:\Lawv^X\to \Lawv^Y$ induced by matrices, which we call \emph{tropical linear}, are exactly those of shape $f(x)=\inf\limits_{b\in Y} \set{\matr f_{a,b}+x_a}$, for some matrix $\matr f$ from $X$ to $Y$.
%\end{remark}

Since $\Lawv$ is a continuous (commutative) semiring, [Proposition III.3, \cite{Manzo2013}] immediately applies and gives:

>>>>

The tropical relational model is thus provided by the category $\LREL$ of matrices with values over $\Lawv$ (which, being a quantale, is indeed a continuous semi-ring).
%, where $\Lawv$ is the already introduced Lawvere quantale, seen as the idempotent complete semiring $(\BB R_{\geq0}\cup\set{\infty},\inf,\infty,+,0)$.
%The category $\LREL$ is well-defined because $\Lawv$ is a continuous semiring (w.r.t.\ its quantale order $\preceq$.
%This amounts to check that $\min$ and $+$ commute with the $\inf$ (as operations on $\BB R_{\geq0}\cup\set{\infty}$, which is immediate), and that $(\Lawv,\preceq)$ is a cpo with $\infty$ as bottom element (which is immediate since in $\Lawv$ we have $\vee = \inf$) .
It is worth observing that the formula for composition in $\LREL$ %is the tropicalisation of the one defining it in $\QREL$, i.e.
reads as \ $(st)_{a,c}:=\inf\limits_{b\in Y}\set{s_{b,c}+t_{a,b}}$;
 similarly, the linear functions $f:\Lawv^X\to \Lawv^Y$ induced by matrices, which we call \emph{tropical linear}, are exactly those of shape $f(x)_b=\inf\limits_{a\in X} \set{\matr f_{a,b}+x_a}$, for some matrix $\matr f$ from $X$ to $Y$.
%\end{remark}

Since $\Lawv$ is a continuous commutative semiring, [Proposition III.3, \cite{Manzo2013}] immediately applies and gives:
